### 2014-03-08 src/analysis.Rnw
update

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Analysis of Sampling Criteria}
% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
\subsubsection{x\% selection}
<<xpercentunit>>=
sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames

#odata <- subset(o.f(stats.xp), s.element=='project')
#rdata <- subset(r.f(stats.xp), s.element=='project')
@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The x\% random selection criteria results.}
\end{table*}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\label{fig:sel}
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\end{figure*}[t]

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\label{fig:sel}
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\end{figure*}[t]

>>>>

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Sampling Criteria}
% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
\subsubsection{x\% selection}
<<xpercentunit>>=
sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames
@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The x\% random selection criteria results.}
\label{tbl:xsel}
\end{table*}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\label{fig:xsamplesel}
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again.

The reduction in mutants for x\% selection using $round(x)$ is graphed in Figure~\ref{fig:xroundsel}. The values for the same are given in Table~\ref{tbl:xsel}

### 2014-03-08 src/methodology.Rnw
update

\begin{table}[h]\footnotesize
\begin{tabular}{ll}
\pitic & Invert negatives \\
\pitrv & Change return values \\
\pitm & Modify arithmetic operators\\
\pitvmc & Remove void method calls \\
\pitnc & Negate conditional statements \\
\pitcb & Modify boundary conditions \\
\piti & Modify increment/decrement \\
\pitnvmc & Replace non-void method calls \\
\pitcc & Replace constructor calls \\
\pitic & Replace inline constants \\
\piti & Remove increment/decrement \\
\pitemv & Replace member variable assignments \\
\pites & Modify switch statements \\
\pitrs & Remove switch elements* \\
\pitrc & Make conditionals true \\
\pitnc & Make conditionas false*
\end{tabular}
\caption{PIT Mutation Opeators}
\label{tbl:pitop}
\end{table}

@@

While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant. For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(x\%, line, 1/64)} is less than 1. We analyzed the results of the following criterias: 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).
% TODO: If the criterias ceil and round does not make sense, we might remove them to gain space.

@@

{\bf Amin: The rest of this section is for Alex and Carlos info and would be omitted later.}

>>>>

\begin{table}[h]\footnotesize
\begin{tabular}{ll}
\pitic & Invert negatives \\
\pitrv & Change return values \\
\pitm & Modify arithmetic operators\\
\pitvmc & Remove void method calls \\
\pitnc & Negate conditional statements \\
\pitcb & Modify boundary conditions \\
\piti & Modify increment/decrement \\
\pitnvmc & Replace non-void method calls \\
\pitcc & Replace constructor calls \\
\pitic & Replace inline constants \\
\piti & Remove increment/decrement \\
\pitemv & Replace member variable assignments \\
\pites & Modify switch statements \\
\pitrs & Remove switch elements* \\
\pitrc & Make conditionals true \\
\pitnc & Make conditionas false* \\
\hline
\end{tabular}
\caption{PIT Mutation Opeators}
\label{tbl:pitop}
\end{table}

@@

While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant. For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(x\%, line, 1/64)} is less than 1. We analyzed the results of the following criterias: 1) to apply \textit{round} function to the resulting number and covert to the nearest integer, and choose that value as the number of mutants (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to apply \textit{sample} criteria suggested by Zhang et al.~\cite{zhang2013ase}, which chooses a mutant with given fracton as probability.
% TODO: If the criterias ceil and round does not make sense, we might remove them to gain space.

@@

{\bf Amin: The rest of this section is for Alex and Carlos info and should be verified if we should include this or wave our hands about approximation instead.}
